
\documentclass[11pt,letterpaper]{report}
\input{preamble.tex}

\begin{document}
    \raggedright{}

    % display your name as the document title
    \namefont{\myname}

    % affiliation and contact info blocks
    \vspace{1em}
    \begin{minipage}[t]{0.700\textwidth}
        % current primary affiliation, left-aligned
        Department of Mathematics \\
       The Ohio State University,  \\
        Columbus, Oh.  
    \end{minipage}\begin{minipage}[t]{0.295\textwidth}
        % contact info details, right-aligned
        \flushright{}
        \href{mailto:meghaichi.1@osu.edu}{meghaichi.1@osu.edu} \\
        \href{https://hmegh.github.io}{hmegh.github.io}
    \end{minipage}


    \section*{Education}

    \begin{tablist}

        \item[Ph.D.] \tab{} Mathematics, Virginia Tech. Advisor: S. Adjerid.
        \tab{} Anticipated graduation: May 2024.
        \item[M.S.]  \tab{} Mathematics, Virginia Tech, 2019.
        \item[B.S.]  \tab{} Mathematics, University of Science and Technology Houari Boumediene, 2016.

    \end{tablist}





    \section*{Research Interests}

    \begin{itemize}

        \item Numerical analysis of partial differential equations. 
        \item Immersed finite element methods for interface problems. 
        \item Fluid-structure interaction problems. 

    \end{itemize}



    \section*{Publications}

    \subsection*{Journal Articles}

    \begin{tablist}

        %\item[\the\year] \tab{}G. Boeing and J. Ha. \textit{Resilient by Design: Simulating Street Network Disruptions across Every Urban Area in the World.} \textit{Transportation Research Part A: Policy and Practice}, under review.

        %\item[\the\year] \tab{}J.~G. Harten and G. Boeing. \textit{Access to the Exclusive City: Home Sharing as an Affordable Housing Strategy.} \textit{Urban Studies}, under review.

        %\item[\the\year] \tab{}C. Higgs, M. Lowe, B. Giles-Corti, G. Boeing\ldots\ and A. Alderton. \textit{Collaborative Development of an Open Science Urban Indicator Toolkit for Assessing Healthy and Sustainable Cities Internationally.} \textit{Environment and Planning B: Urban Analytics and City Science}, under review.

        \item[2024]\tab{} S. Adjerid, T. Lin and H. Meghaichi \textit{Analysis of the Frenet immersed finite element method for  elliptic interface problems} (In progress). 
        

        \item[2024] \tab{}S. Adjerid, T. Lin and H. Meghaichi \textit{A unified immersed finite element error analysis for one-dimensional interface problems} \textit{BIT Numer. Math.}, 63, 13.  \href{https://doi.org/10.1007/s10543-024-01014-z}{ 	doi:10.1007/s10543-024-01014-z}


        \item[2024] \tab{}S. Adjerid, T. Lin and H. Meghaichi \textit{A high order geometry conforming immersed finite element for
        elliptic interface problems} \textit{Comput. Methods Appl. Mech. Engrg.}, 420, 116703. \href{https://doi.org/10.1016/j.cma.2023.116703}{doi:10.1016/j.cma.2023.116703} 

        \item[2023] \tab{}S. Adjerid, T. Lin and H. Meghaichi \textit{An immersed discontinuous Galerkin method for wave propagation in acoustic elastic media.} \textit{J. Comput. Phys.}, 472, 111651. \href{https://doi.org/10.1016/j.jcp.2022.111651}{doi:10.1016/j.jcp.2022.111651} 
    \end{tablist}





    \section*{Invited Talks}

    \begin{tablist}

        \item[2023] \tab{}\textit{A high order  geometry conforming immersed finite element for  elliptic interface problems}. The 8th Annual Meeting of SIAM Central States Section, University of Lincoln-Nebraska.
        
        \item[2023]\tab{}\textit{A unified immersed finite element error analysis for one-dimensional interface problems}. SIAM Southeastern Atlantic Section Annual Meeting, Virginia Tech.
        \item[2021] \tab{}\textit{An immersed discontinuous Galerkin method for wave propagation in acoustic
        elastic media}. The 16th U.S. National Congress on Computational Mechanics, online. 

        \item[2021] \tab{}\textit{An immersed discontinuous Galerkin method for wave propagation in acoustic
        elastic media}.  Finite Element Circus, online.

        \item[2019]\tab{}\textit{An immersed finite element method for wave propagation in acoustic
        elastic media}. Finite Element Circus, Virginia Tech.
    \end{tablist}
        

  
    \subsection*{Campus Talks}

    \begin{tablist}
        \item[2024] \tab{}\textit{
            High order, geometry conforming immersed finite element methods for interface problems. 
        } Applied Numerical Analysis seminar, Virginia Tech. 
        \item[2021] \tab{}\textit{An immersed discontinuous Galerkin method for elastic and
        acoustic-elastic wave propagation}. Applied Numerical Analysis seminar, Virginia Tech. 

        \item[2019]\tab{}\textit{Solution of Coupled Acoustic-Elastic Wave Propagation Problems using an immersed discontinuous Galerkin method}, SIAM student seminar, Virginia Tech.


        %\item[2023] \tab{}\textit{Generalizability in Urban Science.} USC Price School Faculty Seminar Series. Los Angeles, California. Nov 14.

        % \item[2023] \tab{}\textit{Resilient by Design: Simulating Street Network Disruptions across Every Urban Area in the World.} METRANS University Transportation Center Speaker Series. Los Angeles, California. Nov 2.



    \end{tablist}



    

   

   
    \section*{Awards and Honors}


    \begin{tablist}
        \item[2023] \tab{}SIAM Student travel award. 

        \item[2022] \tab{}Lee R. Steeneck and Regina Aultice Steeneck Graduate Fellowship (\$8,875). College of Science, Virginia Tech. 
        

        \item[2021] \tab{}Outstanding Graduate Teaching Assistant Award. Department of Mathematics, Virginia Tech.
        
        \item[2021]\tab{}US National Congress for Computational Mechanics Conference Award.
      

    \end{tablist}

   


\section*{Courses Taught}
    % \subsection*{Virginia Tech}
    \begin{tablist}
        \item[MATH 4564] \tab{}{Operational methods: Laplace/Fourier transform and partial differential equations.}
        
        \hfill (Summer 20, F20, S21, Summer 21, F21, S22,
        Summer 22, F22, Summer 23)

        \item[MATH 4446] \tab{}{Numerical analysis: Interpolation, quadrature and numerical ODEs.  }
        \hfill (Summer 20)
        \item[MATH 2204]\tab{}{Introduction to multivariable calculus. }
        \hfill (Summer 19)

        \item[MATH 2114]\tab{}{Introduction to linear algebra. }
        \hfill (S20, S24)
        \item[MATH 1226]\tab{}{Calculus II.}
        \hfill (S19) 

        \item[MATH 1225]\tab{}{Calculus I.} \hfill 
        (F18, F19, Summer 21, Summer 22, Summer 23, F23)
    \end{tablist}
        
    


    \section*{Service}

  

    \subsection*{Academic Journal Peer Review}

    \begin{itemize}
      \item International Journal of Modelling and Simulation, Taylor \& Francis.
    \end{itemize}

    \subsection*{Departmental service and outreach}

   \begin{tablist}
    \item[-] President, SIAM Student Chapter (2018-2019): As the president of the student chapter, I was in charge of organizing  biweekly
    research seminars, which provided a platform for Virginia Tech graduate students, professors, and alumni to present their work.

    \item[-] Senior Graduate Teaching assistant (2019-2022): I was responsible for co-organizing a biweekly seminar covering a spectrum of subjects ranging
    from teaching to personal development.

    \item[-] Mentoring new graduate teaching assistant: I have facilitated the teaching certification process for four graduate students, offering them hands-on classroom teaching opportunities and consistent feedback to help them refine their skills.

    \item[-] Volunteer at \href{http://intranet.math.vt.edu/MORE/}{MORE '19} and \href{https://intranet.math.vt.edu/MORE2020/}{MORE '20}: As a graduate student participant at MORE, I had the chance to share my research experience with aspiring undergraduate students from different universities. 
   \end{tablist}


    % display today's date as Month Year after a vertical space below the end of the text
    \begin{center}
        \vfill
        Updated \monthyeardate\today
    \end{center}

\end{document}